Detecting Treatment-Subgroup Interactions in Clustered Data with Generalized Linear Mixed-Effects Model Trees

### 2015-09-07 pkg/glmertree/paper/treatment_interactions.Rnw
added workaround for the situation where the random effects part also contains fixed effects: instead of omitting only the random effects from the offset prediction now the coefficients from the .tree are set to 0
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@780 255f4249-2263-4417-b1ea-8498779e27a7

## GLM tree (estimated via lmertree to determine offset iteratively)
## lmtree_app <- lmtree(HRSDt1 ~ Tx_group | Age + Gender + education + ComorbidAnxietyDisorder + HRSDt0,
##   data = metadata, offset = hrs)
lmtree_app <- lmertree(HRSDt1 ~ Tx_group | HRSDt0 | Age + Gender + education + ComorbidAnxietyDisorder + HRSDt0,
  data = metadata, ranefstart = hrs, joint = FALSE)

## GLMM tree (estimated with joint = FALSE because fixed effect HRSDt0 is included in random formula)
lmertree_app <- lmertree(HRSDt1 ~ Tx_group | (1 | studyid) + HRSDt0 | Age + Gender + education + ComorbidAnxietyDisorder + HRSDt0,
  data = metadata, ranefstart = hrs, joint = FALSE)
@

>>>>

## GLM tree (estimated via lmertree to determine offset iteratively)
## lmtree_app <- lmtree(HRSDt1 ~ Tx_group | Age + Gender + education + ComorbidAnxietyDisorder + HRSDt0,
##   data = metadata, offset = hrs)
lmtree_app <- lmertree(HRSDt1 ~ Tx_group | HRSDt0 | Age + Gender + education + ComorbidAnxietyDisorder + HRSDt0,
  data = metadata, ranefstart = hrs)

## GLMM tree (estimated with joint = FALSE because fixed effect HRSDt0 is included in random formula)
lmertree_app <- lmertree(HRSDt1 ~ Tx_group | (1 | studyid) + HRSDt0 | Age + Gender + education + ComorbidAnxietyDisorder + HRSDt0,
  data = metadata, ranefstart = hrs)
@
